\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Outline}
\author{Christina Catlett, Daniel Shenker, Rachel Wander, Maya Watanabe}
\date{June 2020}

\begin{document}

\maketitle

\section{Introduction}
\begin{enumerate}
    \item Bringing dynamical systems and parametrization together.
    \item Current knowledge of the following parametrization techniques
    \begin{itemize}
        \item MCMC
        \item PSO
        \item UKF
    \end{itemize}
    \item Introduction of the Biological Systems utilized in the paper.
    \begin{itemize}
        \item Lotka Volterra
        \item T1D
        \item Why have we chosen these systems?
    \end{itemize}
    \item Overview of parametrization.
    \begin{itemize}
        \item Overall goal.
        \item High level explanation of each algorithm.
    \end{itemize}
    
\end{enumerate}

\section{Problem Set-up}
\begin{enumerate}
    \item Lotka Volterra
    \item T1D
    \item For each, describe elements of the model, include general figures describing them, and discuss the data sources.
\end{enumerate}

\section{MCMC}
\begin{enumerate}
    \item Theoretical background
    \item General Tutorial
    \item Application to Lotka-Volterra
    \item Application to T1D
\end{enumerate}

\section{Kalman Filter}
\begin{enumerate}
    \item Theoretical background
    \item General Tutorial
    \begin{itemize}
        \item Joint
        \item Dual
    \end{itemize}
    \item Application to Lotka-Volterra
    \begin{itemize}
        \item Joint
        \item Dual
    \end{itemize}
    \item Application to T1D
    \begin{itemize}
        \item Joint
        \item Dual
    \end{itemize}
\end{enumerate}

\section{Discussion}
\begin{enumerate}
    \item Each algorithm gives overview of their findings
    \begin{itemize}
        \item MCMC
        \begin{itemize}
            \item What we learned
            \item Next steps
        \end{itemize}
        \item PSO
        \item UKFs
    \end{itemize}
    \item General improvements to techniques moving forward.
    \begin{itemize}
        \item Error quantification - Christina
        \item Sensitivity analysis - 
    \end{itemize}
    \item Combination of MCMC and UKF algorithms - Maya
    \item Future Applications (mostly in context of T1D for now) - Daniel
\end{enumerate}


\section{References}
\section{Appendix}

\end{document}